Proving Atomic Specifications for Data Structures with Fine-Grained Locking

### 2022-01-28 concurrency/ITP 2022/Verification of Concurrent Binary Search Tree.tex
starting to rewrite ITP submission

\title{Verifying Fine-Grained and Lock-Free Binary Search Trees}
\author{Roshan Sharma}{University of Illinois at Chicago, USA}{}{}{}
\author{Shengyi Wang}{Princeton University, USA}{}{}{}
\author{Alexander Oey}{, USA}{}{}{}
\author{Anastasiia Evdokimova}{University of Illinois at Chicago, USA}{}{}{}
\author{Lennart Beringer}{Princeton University, USA}{}{}{}
\author{William Mansky}{University of Illinois at Chicago, USA}{}{}{}

@@

This invariant becomes slightly more complicated when we consider \emph{ownership} of locks, as is required if we want to eventually free the lock and return its resources. In this case the lock assertion carries a share $\pi$, where the full share $\pi = 1$ is required to free the lock, while any share is sufficient to acquire or release it. We can amend our lock invariant to $R(n) \triangleq n \mapsto (d, n', \ell') * \ell' \islock_\pi R(n')$ for some suitable share $\pi$, but then, what happens to the share of $n_1$'s lock when we release the lock on $n$? Starting from a state in which we hold $n$'s lock $\ell$, this gives us:
\begin{align*}
&\{ \ell \islock_\pi R(n) * n \mapsto (d, n', \ell') * \ell' \islock_\pi R(n') \}\\
&\texttt{acquire}(\ell');\\
&\{ \ell \islock_\pi R(n) * n \mapsto (d, n', \ell') * \ell' \islock_\pi R(n') * n' \mapsto (d, n'', \ell'') * \ell'' \islock_\pi R(n'') \}\\
&\texttt{release}(\ell);\\
&\{ \ell \islock_\pi R(n) * n' \mapsto (d, n'', \ell'') * \ell'' \islock_\pi R(n'') \}
\end{align*}
In order to re-establish $\ell$'s lock invariant $R(n)$, we must give up our knowledge of $n'$'s lock $\ell'$. This leaves us with two problems: we have no lock assertion for $\ell'$, so we will be unable to release it later, and we still have partial ownership of $\ell$'s lock assertion, without any way to re-collect our share. Both of these problems can be solved by making the lock \emph{recursive}, including a share of the lock assertion in its own lock invariant\footnote{Gotsman et al. instead use a separation assertion $\mathsf{Locked}$ that is always held by the thread that acquires a lock, and is required to free the lock: this is equivalent to an extra share of the lock assertion.}:
$$R(n) \triangleq \ell \islock_{\pi_1} R(n) * n \mapsto (d, n', \ell') * \ell' \islock_{\pi_2} R(n')$$

@@

\subsection{Atomic Specifications}
\label{atomic}
For many concurrent data structures, the ideal correctness condition is that the data structure behaves the same as a sequential implementation, even when accessed simultaneously by multiple threads. This intuitive condition can be formalized as linearizability (operations appear to take effect in some total order) or atomicity (client threads never observe intermediate states of operations). In separation logic, atomicity can be expressed in the form of \emph{atomic triples}~\cite{tada}, written in the form $\forall a.\ \langle P_l\ |\ P_p(a)\rangle\ c\ \langle Q_l\ |\ Q_p(a)\rangle$, where $P_l$ and $Q_l$ are \emph{private} pre- and postconditions similar to an ordinary Hoare triple, and $P_p$ and $Q_p$ are \emph{public} pre- and postconditions, parameterized by an abstract value $a$ of the shared data structure. Intuitively, $P_l$ and $Q_l$ must be true before and after the call, while $P_p$ must be true for some value of $a$ at every point from the beginning of $c$ until some designated linearization point, at which point $Q_p$ becomes true atomically for the same value $a$. For instance, the specification $$\forall s.\ \langle \mathsf{is\_stack}\ p\ |\ \mathsf{stack}\ s\rangle\ \texttt{push}(v)\ \langle \mathsf{is\_stack}\ p\ |\ \mathsf{stack}\ (v :: s)\rangle$$ expresses the fact that the \texttt{push} operation of a concurrent stack correctly implements the behavior of a sequential push, atomically transitioning from some stack $s$ to $v :: s$ at some point during its execution. %maybe something about linking ghost state, which parts are real vs. ghost, accessing invariants around atomic triple

@@

\ignore{\section{Safety Proofs} %maybe cut this, or roll it into the next section
\label{safety}

In this section, we will focus on safety proofs of concurrent binary search tree. Here safety means thread-safe. An operation of any concurrent data-structure is thread-safe if it functions correctly during simultaneous execution by multiple threads. A thread can update the data structure if it holds a sufficiently large share of the data structure so that no other thread can possibly read it. If we want to have a data structure that can be modified by multiple threads, we must move shares between threads via locks. In VST, we can use $\mathsf{lock\_inv}$ assertion to assert that there exists a lock in memory with a given invariant: $\mathsf{lock\_inv}\ \mathsf{sh}\ p\ R$ means that the current thread owns share $\mathsf{sh}$ of a lock at location $p$ with invariant $R$. We use the term \emph{lock invariant} for $R$, which is a predicate representing the resources protected by a lock. The $\mathsf{lock\_inv}$ predicate is sufficient to prove the safety properties of the concurrent data-structure.

%We have taken binary search tree with fine-grained locking. In hand-over-hand locking mechanism, we acquire the lock for a successor before releasing the lock for a predecessor. The code for $\texttt{insert}$ and $\texttt{lookup}$ methods of concurrent binary search tree that we are interested to verify is presented in Figure 1.

\subsection{Specification and Verification}
We begin the verification by defining a predicate $\nodeboxrep(p)$ that describes the concrete representation of the tree, where $p$ is the pointer to the root node. The $\texttt{nodebox\_rep}$ predicate ties together $\texttt{lock\_inv}$ assertion for each recursive lock as follows: 
\begin{align*}
 &\nodeboxrep_{\pi}(p) \triangleq  p\mapsto\ (lock,tp)\ *\ \mathsf{lock\_inv_{\pi}}(lock, \mathsf{selflock}_{0.5}(lock,R))) \\&R  \triangleq\ \exists\ pa\ pb\ \ tp\mapsto\ (pa * pb)\ *\  \nodeboxrep_{0.5}(pa)\ *\ \nodeboxrep_{0.5}(pb)  \end{align*}

 The ownership of each node's lock is divided into two halves: one half is owned by \emph{lock\ invariant} and another half is owned by node itself. But, in case of root node, we need to split one half into multiple pieces, and share those pieces to all threads such that all of them initially have the knowledge of root node.

 The \emph{lock}, used in the implementation of BST operations, provides \texttt{acquire} and \texttt{release} functions, which allow threads to transfer ownership of resource invariants. Their pre- and postconditions are as follows:
$$\{!!\mathsf{readable\_share}\ \mathit{sh} \land \mathsf{lock\_inv}\ \mathit{sh}\ \ell\ R\}\ \texttt{acquire}(\ell)\ \{R * \mathsf{lock\_inv}\ \mathit{sh}\ \ell\ R\}$$
$$\{!!(\mathsf{readable\_share}\ \mathit{sh} \land \mathsf{exclusive}\ R) * R * \mathsf{lock\_inv}\ \mathit{sh}\ \ell\ R\}\ \texttt{release}(\ell)\ \{\mathsf{lock\_inv}\ \mathit{sh}\ \ell\ R\}$$

The resource invariant $R$ need to be \emph{exclusive}, i.e, it can only hold once in any given state. This allows us to know that if the current thread holds the invariants, it also hold the lock. 
}

@@

\forall m.\ \langle \nodeboxrep\ p\ |\ \treerep\ m\rangle\ \texttt{delete}(p, k)\ \langle \nodeboxrep\ p\ |\ \treerep\ (\mathrm{delete}\ m\ k)\rangle
\end{mathpar}
where $\treerep(m)$ asserts that global ghost state of the tree implements a map $m$, as described above, and $\nodeboxrep$ (the client's handle to the data structure) is simply a reference to the lock variant for the root node:
$$\nodeboxrep(b) \triangleq \exists p.\ b \mapsto p * p.\texttt{lock} \lockvar \mathsf{node\_inv}$$
Now we are prepared to prove that each of our BST functions satisfies its specification.

@@

The function has two possible linearization points: after line 23, where we finish adding a node $(k, v)$ to the tree, and after line 41, where we change the value of an existing node with key $k$ to $v$. In both cases, we use the \textsf{sync\_commit} rule to atomically update the abstract state of the data structure from $\treerep m$ to $\treerep (\mathrm{insert}\ m\ k\ v)$, by showing that the update to the tree implementation corresponds to a local change in the abstract tree that implements the mathematical $\mathsf{insert}$. In the first case, the local change is the insertion of $(k, v)$ at an empty leaf whose range includes $k$, and the addition of two new empty leaves as its children; in the second case, we simply change the value of an internal node whose key is already $k$. Our higher-level proofs, then, need to show that these two changes are both valid operations on ghost trees that yield the desired insertion in the global state.

@@

\section{Related Work}
\label{related}
Our work is based on the concurrent separation logic of VST in the style of Iris \cite{higherorderghoststate} and the logical atomicity from TaDA logic  \cite{tada}. The notion of the \emph{lower} and \emph{upper} bound is taken from the flow interface paper \cite{krishna2017flow}. Our main technical contributions are the verification of two different implementation of binary search tree (using fine-grained locking and lock-free technique) with respect to the same abstract specification, and first c-level mechanized verification of concurrent search-based data structure (i.e. BST). Most of the other concurrent separation logic (CSL)-based verification works are on toy languages, while VST lets us use the same logic on real C programs.

Gotsman and Yang \cite{gotsman} is one of the earliest work on concurrent separation logic. They introduced the program logic to reason locally about the heap-manipulating program with the notion of dynamic ownership of heap parts by unbounded number of locks and threads, and shown the verification of singly-linked list with fine-grained locking. Xiong et al. \cite{Xiong2017Abstract} have demonstrated the verification of ConcurrentSkipListMap from java.util.concurrent library using the recent advances in fine-grained concurrency reasoning. Their work is mainly based on the abstract atomicity from TaDa logic, and give two modular specifications for concurrent maps: one specification focus on the entire map structure which is suitable for verifying implementation, and another specification focus on the key-value pairs which appropriate for verifying clients. We use the same idea of atomicity (though implemented in Iris) in our work.

>>>>

\title{Proving Atomic Specifications for Data Structures with Fine-Grained Locking}
\author{Roshan Sharma}{University of Illinois at Chicago, USA}{}{}{}
\author{Shengyi Wang}{Princeton University, USA}{}{}{}
\author{Alexander Oey}{, USA}{}{}{}
\author{Anastasiia Evdokimova}{University of Illinois at Chicago, USA}{}{}{}
\author{Lennart Beringer}{Princeton University, USA}{}{}{}
\author{William Mansky}{University of Illinois at Chicago, USA}{}{}{}

@@

This invariant becomes slightly more complicated when we consider \emph{ownership} of locks, as is required if we want to eventually free the lock and return its resources. In this case we the lock assertion carries a share $\pi$, where the full share $\pi = 1$ is required to free the lock, while any share is sufficient to acquire or release it. We can amend our lock invariant to $R(n) \triangleq n \mapsto (d, n', \ell') * \ell' \islock_\pi R(n')$ for some suitable share $\pi$, but then, what happens to the share of $n_1$'s lock when we release the lock on $n$? Starting from a state in which we hold $n$'s lock $\ell$, this gives us:
\begin{align*}
&\{ \ell \islock_\pi R(n) * n \mapsto (d, n', \ell') * \ell' \islock_\pi R(n') \}\\
&\texttt{acquire}(\ell');\\
&\{ \ell \islock_\pi R(n) * n \mapsto (d, n', \ell') * \ell' \islock_\pi R(n') * n' \mapsto (d, n'', \ell'') * \ell'' \islock_\pi R(n'') \}\\
&\texttt{release}(\ell);\\
&\{ \ell \islock_\pi R(n) * n' \mapsto (d, n'', \ell'') * \ell'' \islock_\pi R(n'') \}
\end{align*}
In order to re-establish $\ell$'s lock invariant $R(n)$, we must give up our knowledge of $n'$'s lock $\ell'$. This leaves us with two problems: we have no lock assertion for $\ell'$, so we will be unable to release it later, and we still have partial ownership of $\ell$'s lock assertion, without any way to re-collect our share. Both of these problems can be solved by making the lock \emph{recursive}, including a share of the lock assertion in its own lock invariant\footnote{Gotsman et al. instead use a separation assertion $\mathsf{Locked}$ that is always held by the thread that acquires a lock, and is required to free the lock: this is equivalent to an extra share of the lock assertion.}:
$$R(n) \triangleq \ell \islock_{\pi_1} R(n) * n \mapsto (d, n', \ell') * \ell' \islock_{\pi_2} R(n')$$

@@

\subsection{Atomic Specifications}
\label{atomic}

For many concurrent data structures, the ideal correctness condition is that the data structure behaves the same as a sequential implementation, even when accessed simultaneously by multiple threads. This intuitive condition can be formalized as linearizability (operations appear to take effect in some total order) or atomicity (client threads never observe intermediate states of operations). In separation logic, atomicity can be expressed in the form of \emph{atomic triples}~\cite{tada}, written in the form $\forall a.\ \langle P_l\ |\ P_p(a)\rangle\ c\ \langle Q_l\ |\ Q_p(a)\rangle$, where $P_l$ and $Q_l$ are \emph{private} pre- and postconditions similar to an ordinary Hoare triple, and $P_p$ and $Q_p$ are \emph{public} pre- and postconditions, parameterized by an abstract value $a$ of the shared data structure. Intuitively, $P_l$ and $Q_l$ must be true before and after the call, while $P_p$ must be true for some value of $a$ at every point from the beginning of $c$ until some designated linearization point, at which point $Q_p$ becomes true atomically for the same value $a$. For instance, the specification $$\forall s.\ \langle \mathsf{is\_stack}\ p\ |\ \mathsf{stack}\ s\rangle\ \texttt{push}(v)\ \langle \mathsf{is\_stack}\ p\ |\ \mathsf{stack}\ (v :: s)\rangle$$ expresses the fact that the \texttt{push} operation of a concurrent stack correctly implements the behavior of a sequential push, atomically transitioning from some stack $s$ to $v :: s$ at some point during its execution. %maybe something about linking ghost state, which parts are real vs. ghost, accessing invariants around atomic triple

@@

\section{Locks and Atomicity}

@@

\forall m.\ \langle \nodeboxrep\ p\ |\ \treerep\ m\rangle\ \texttt{delete}(p, k)\ \langle \nodeboxrep\ p\ |\ \treerep\ (\mathrm{delete}\ m\ k)\rangle
\end{mathpar}
where $\treerep\ m$ asserts that global ghost state of the tree implements a map $m$, as described above, and $\nodeboxrep$ (the client's handle to the data structure) is simply a reference to the lock variant for the root node:
$$\nodeboxrep(b) \triangleq \exists p.\ b \mapsto p * p.\texttt{lock} \lockvar \mathsf{node\_inv}$$
Now we are prepared to prove that each of our BST functions satisfies its specification.

@@

The function has two possible linearization points: after line 23, where we finish adding a node $(k, v)$ to the tree, and after line 41, where we change the value of an existing node with key $k$ to $v$. In both cases, we use the \textsf{sync\_commit} rule to atomically update the abstract state of the data structure from $\treerep\ m$ to $\treerep (\mathrm{insert}\ m\ k\ v)$, by showing that the update to the tree implementation corresponds to a local change in the abstract tree that implements the mathematical $\mathsf{insert}$. In the first case, the local change is the insertion of $(k, v)$ at an empty leaf whose range includes $k$, and the addition of two new empty leaves as its children; in the second case, we simply change the value of an internal node whose key is already $k$. Our higher-level proofs, then, need to show that these two changes are both valid operations on ghost trees that yield the desired insertion in the global state.

@@

\section{Related Work}
\label{related}
Our work is based on the concurrent separation logic of VST in the style of Iris \cite{higherorderghoststate} and the logical atomicity from TaDA logic  \cite{tada}. The notion of the \emph{lower} and \emph{upper} bound is taken from the flow interface paper \cite{krishna2017flow}. Our main technical contributions are the verification of two different implementation of binary search tree (using fine-grained locking and lock-free technique) with respect to the same abstract specification, and first c-level mechanized verification of concurrent search-based data structure (i.e. BST). Most of the other concurrent separation logic (CSL)-based verification works are on toy languages, while VST lets us use the same logic on real C programs.  VeriFast~\cite{verifast-conc} also operates on C code, albeit without a full formal semantics of C.

Gotsman and Yang \cite{gotsman} is one of the earliest work on concurrent separation logic. They introduced the program logic to reason locally about the heap-manipulating program with the notion of dynamic ownership of heap parts by unbounded number of locks and threads, and shown the verification of singly-linked list with fine-grained locking. Xiong et al. \cite{Xiong2017Abstract} have demonstrated the verification of ConcurrentSkipListMap from java.util.concurrent library using the recent advances in fine-grained concurrency reasoning. Their work is mainly based on the abstract atomicity from TaDA logic, and give two modular specifications for concurrent maps: one specification focus on the entire map structure which is suitable for verifying implementation, and another specification focus on the key-value pairs which appropriate for verifying clients. We use the same idea of atomicity (though implemented in Iris) in our work.

### 2022-01-28 concurrency/ITP 2022/intro.tex
starting to rewrite ITP submission

% Contributions:
% verified C implementation of BST -- the first?
% technique for connecting locks with abstract state/atomicity
% VST-style decomposition of proofs into C-to-local-abstract and local-to-global-abstract
% lock-free implementation?

The binary search tree (BST) is a common implementation of an ordered
map, a widely used data structure. The concurrent version of the
ordered map forms the bedrock of many parallel programs. We formally
verified the functional correctness of two versions of fine-grained
concurrent binary search trees (CBST) written in C. One adopts the
hand-over-hand locking technique \cite{bayer1977}, the other is lock
free by using atomic primitives such as compare and swap (CAS). Both
CBST implementations support insert, lookup, and delete operations; %or do we have lock-free without delete?
they also share the ``same'' specifications to some extent in our
verification. All the proof is machine-checked in Coq. %Say something about existing proofs of fine-grained data structures and how we compare.

Our specifications use the logical atomicity introduced in the TaDA
logic \cite{tada}, in the form of \emph{atomic Hoare
triples}. Intuitively, an atomic Hoare triple $ \langle
P \rangle\,\mathbb{C}\, \langle Q \rangle$ means the program
$\mathbb{C}$ ``atomically updates'' from $P$ to $Q$. The program may
actually take multiple steps, but every step before the atomic update
(linearization point) must preserve the assertion $P$. Meanwhile, the
concurrent environment may also update the state before the
linearization point, as long as the states satisfies $P$. The
assertion $Q$ must become true at the linearization point, then the
environment can do whatever it likes. There is no guarantee that $Q$
is still preserved when $\mathbb{C}$ returns. For example, the
specification of our \texttt{insert} operation may be explained as
follows: during the execution of \texttt{insert}, there is
always \emph{some} BST, and at some point the \texttt{insert} will
take a BST $t$, insert a value with a certain key, and then eventually
returns (meanwhile other threads may have further modified the
inserted tree).

We employ the Verified Software Toolchain (VST) \cite{plfcc} to verify
the correctness of CBST. Although the concurrent separation logic
(CSL) has been formalized in VST rooted on the work of Hobor et
al.\ \cite{oraclesematic}, we extend it with two descendants of CSL so
as to accomplish the verification. One is the logical atomicity
mentioned above; the other is the higher-order ghost state in the
style of Iris \cite{higherorderghoststate}. The ghost states are used
to construct both the global invariants and the local state in our
proofs. They will be further discussed in \S\ref{correctness}.

We highlights a few innovative aspects about our verification of CBST:
\begin{description}
\item [Range ghost] We abstract the BST via a pair of values
called \emph{range} which represents the lower-bound and upper-bound
of keys on each node to reason about the BST in the current
settings. We prove that range with the merging operation forms a
partial commutative monoid (PCM) so that it can be encoded in ghost
states.

\item [\textsf{sync\_inv} pattern] It is a particular approach
combining locks with general invariants to solve the dilemma caused by
the fine-grained locking mechanism: we do not have a lock to control
the access of the entire BST nor can we access the state of the BST
via atomic operations.
\end{description}

%% Do we have contributions, and are they sufficient? Range ghost is adapted from flow interfaces. Sync_inv pattern isn't totally ours, though it might be instructive w.r.t. combining traditional and Iris-style CSLs, and it might be worth explaining in more detail. We're working on "actual" code, but missing a few pieces to make our proofs foundational. (but maybe it's worth highlighting the extra work we do to work on actual code) We could promote this as the first working example of Iris+VST. We don't yet have any demonstrations on larger or interesting data structures, and this alone was quite a bit of work. The delete logic is rather interesting. Nothing to say about flow interfaces yet, but maybe soon.

Our specific contributions are:
\begin{itemize}
\item To the best of our knowledge, this is the first mechanized
verification of an concurrent search-based data structure written in a
real programming language. %should probably clarify what we mean by "real"

\item We illustrate how to incorporate the CSL in VST, the higher-order
ghost state in the style of Iris, and the logical atomicity from the
TaDA logic together to verify the CBST.
\end{itemize}

We introduce the background about the verification of concurrent C
programs in \S\ref{background}, including the tool-chain VST and Iris,
the concept of ghost states, global invariants, and atomic
specifications. The thread-safety proofs of operations on CBST are
first explained in \S\ref{safety}, where we show the \emph{recursive}
lock pattern for hand-over-hand locking mechanism. The functional
correctness proofs are presented in \S\ref{correctness}. We detail the
use of the \textsf{sync\_inv} pattern, the combination of recursive
lock invariants and ghost states together in the atomic
specifications, and the proof skeleton of each operation on CBST. The
related work is discussed in \S\ref{related}. We end with the
conclusion of our work in \S\ref{conclusion}.

>>>>

% Contributions:
% verified C implementation of BST with atomic specs -- the first? VeriFast did it, but not atomic specs
% technique for connecting locks with abstract state/atomicity
% VST-style decomposition of proofs into C-to-local-abstract and local-to-global-abstract
% delete proofs -- interesting interplay between non-visible range increase and lock-protected range modification
% lock-free implementation?

% start with atomic specs for cglock implementation, where the local ghost state *is* the global ghost state!

Concurrent separation logic~\cite{csl} is a useful tool for proving correctness of concurrent programs. While early iterations focused on data structures implemented with locks~\cite{gotsman, oraclesematic} and specifications involving memory safety and data-race-freedom, more recent logics are able to prove linearizability-style functional correctness~\cite{tada} of lock-free implementations that use low-level atomic memory operations~\cite{iris}, even under weak memory models~\cite{gps, rsl}. In particular, \emph{logical atomicity}~\cite{tada} has become the gold standard for concurrent data structure specifications, capturing the idea that data structure operations should appear to take place instantaneously with no externally visible intermediate states. The effects of a logically atomic operation become visible at a \emph{linearization point}, a single instruction (usually an atomic memory operation or call to a logically atomic function) that publishes the new state of the data structure.

Intuitively, a critical section in a lock-based implementation serves the same role as an atomic instruction in a lock-free data structure, and it is not hard to identify linearization points in lock-based implementations---the effects of an update become visible when the lock protecting the updated data is released. In practice, however, the interaction between traditional lock-based separation logic and atomic specifications has been underexplored. In this paper, we demonstrate an approach to proving that lock-based implementations of data structures satisfy logically atomic specifications. The approach has two main components. First, we associate each lock with a piece of ghost state representing the abstract state of the part of the data structure it protects. In a \emph{coarse-grained} implementation, where a single lock protects the entire data structure, this is sufficient (in combination with proof rules for logical atomicity) to prove that operations complete atomically. In a \emph{fine-grained} implementation, however, a lock may only protect a small piece of the data structure (a single node in a tree, for instance), and the overall state of the data structure may be composed of a large number of per-lock abstract states. For these data structures, our second step is to prove lemmas describing how changes to local abstract state propagate to change (or maintain) the global abstract state. This gives us a two-layer verification process: we prove that the code of each function implements some local changes to the abstract state, and separately we prove that these local changes implement a global change.

Our proof technique is implemented in the Verified Software Toolchain~\cite{plfcc}, a system for proving separation logic properties of C programs, so we can prove correctness of C implementations of lock-based concurrent data structures. We take advantage of recent extensions to VST to include Iris-style ghost state and logically atomic specifications~\cite{vst-iris}. We demonstrate our technique by proving the correctness of a binary search tree with hand-over-hand locking. %something about client

%Our specific contributions are:
%\begin{itemize}
%\item To the best of our knowledge, this is the first mechanized
%verification of a concurrent search-based data structure written in a
%real programming language. %should probably clarify what we mean by "real"

%\item We illustrate how to incorporate the CSL in VST, the higher-order
%ghost state in the style of Iris, and the logical atomicity from the
%TaDA logic together to verify the CBST.
%\end{itemize}

%We introduce the background about the verification of concurrent C
%programs in \S\ref{background}, including the tool-chain VST and Iris,
%the concept of ghost states, global invariants, and atomic
%specifications. The thread-safety proofs of operations on CBST are
%first explained in \S\ref{safety}, where we show the \emph{recursive}
%lock pattern for hand-over-hand locking mechanism. The functional
%correctness proofs are presented in \S\ref{correctness}. We detail the
%use of the \textsf{sync\_inv} pattern, the combination of recursive
%lock invariants and ghost states together in the atomic
%specifications, and the proof skeleton of each operation on CBST. The
%related work is discussed in \S\ref{related}. We end with the
%conclusion of our work in \S\ref{conclusion}.
